---
title: "Business Dashboard"
pagetitle: "Dashboard — Saad Al Awadhi"
format:
  dashboard:
    theme:
      - cosmo
      - styles.scss
    orientation: rows
    nav-buttons:
      - icon: house
        href: index.html
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
library(ggplot2)

PETROL <- "#0d3b45"; COPPER <- "#c07a43"; STEEL <- "#2a7080"; MUTED <- "#6b7671"

theme_dash <- function(base_size = 12) {
  theme_minimal(base_size = base_size) +
    theme(
      legend.position = "none",
      panel.grid.minor = element_blank(),
      plot.background = element_rect(fill = NA, color = NA),
      panel.background = element_rect(fill = NA, color = NA)
    )
}
```

## Row {height=25%}

::: {.valuebox icon="shop" color="#0d3b45"}
Ventures founded

**2**
:::

::: {.valuebox icon="globe" color="#2a7080"}
Markets

**2**
:::

::: {.valuebox icon="people" color="#c07a43"}
Clients

**100+**
:::

::: {.valuebox icon="graph-up-arrow" color="#1a5560"}
Languages

**2**
:::

## Row {height=38%}

### Column {width=55%}

#### Monthly sourcing volume (illustrative index)

```{r}
#| fig-width: 7
#| fig-height: 3.6
df <- data.frame(
  month = factor(month.abb, levels = month.abb),
  vol = c(42,48,55,53,61,66,72,70,78,85,92,98)
)
ggplot(df, aes(as.integer(month), vol)) +
  geom_area(fill = PETROL, alpha = 0.10) +
  geom_line(color = PETROL, linewidth = 1) +
  geom_point(color = PETROL, size = 2) +
  scale_x_continuous(breaks = 1:12, labels = month.abb) +
  labs(x = NULL, y = "Volume index") +
  theme_dash() +
  theme(panel.grid.major.x = element_blank())
```

### Column {width=45%}

#### Category margin profile

```{r}
#| fig-width: 5.6
#| fig-height: 3.6
df <- data.frame(
  cat = factor(c("Health/Beauty","Kitchen","Grocery","Electronics","Closeout"),
               levels = rev(c("Health/Beauty","Kitchen","Grocery","Electronics","Closeout"))),
  margin = c(22,18,12,15,28)
)
cols <- rev(c(PETROL, STEEL, MUTED, STEEL, COPPER))
ggplot(df, aes(margin, cat, fill = cat)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = paste0(margin, "%")), hjust = -0.3, size = 3, color = "#1c2529") +
  scale_fill_manual(values = cols) +
  scale_x_continuous(limits = c(0, 32), expand = c(0, 0)) +
  labs(x = "Avg. gross margin (%)", y = NULL) +
  theme_dash() +
  theme(panel.grid.major.y = element_blank())
```

## Row {height=37%}

### Column {width=50%}

#### Customer acquisition funnel

```{r}
#| fig-width: 6
#| fig-height: 3.4
df <- data.frame(
  stage = factor(c("Reach","Visits","Cart","Purchase","Repeat"),
                 levels = rev(c("Reach","Visits","Cart","Purchase","Repeat"))),
  value = c(100,42,18,9,4)
)
cols <- rev(c(PETROL, STEEL, STEEL, COPPER, "#d59a6b"))
ggplot(df, aes(value, stage, fill = stage)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = value), hjust = -0.3, size = 3, color = "#1c2529") +
  scale_fill_manual(values = cols) +
  scale_x_continuous(limits = c(0, 110), expand = c(0, 0)) +
  labs(x = "Index (Reach = 100)", y = NULL) +
  theme_dash() +
  theme(panel.grid.major.y = element_blank())
```

### Column {width=50%}

#### Lead-gen pipeline throughput

```{r}
#| fig-width: 6
#| fig-height: 3.4
df <- data.frame(week = 1:8, leads = c(120,145,160,180,175,205,230,255))
ggplot(df, aes(week, leads)) +
  geom_col(fill = PETROL, width = 0.7) +
  scale_x_continuous(breaks = 1:8) +
  labs(x = "Week", y = "Qualified leads") +
  theme_dash() +
  theme(panel.grid.major.x = element_blank())
```

::: {.card}
Figures on this dashboard are illustrative and demonstrate the reporting approach used to manage S&N Supplies and Impact Lights.
:::
